---
title: "FEISTY method figures"
format: html
editor: visual
date: today
---

## Install FEISTY:

Download and install FEISTY package from GitHub. Devtools is required:

```{r}
#| warning: FALSE
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}

if (!requireNamespace("FEISTY", quietly = TRUE)) {
devtools::install_github("https://github.com/Kenhasteandersen/FEISTY/tree/R-Package")
}
```

## Prepare environment:

Clear environment:

```{r}
rm(list = ls())
```

Load packages:

```{r}
#| output: false
library(tidyverse)
library(FEISTY)
library(mgcv)
library(patchwork)
library(png)
library(foreach)
library(doParallel)
library(rnaturalearth)
library(sf)
library(viridis)
```

## Create figures:

### Figure 2:

Run and plot a simple model example:

```{r}
parameters = setupVertical2(nStages = 9)
sim = simulateFEISTY(p = parameters)
plotSimulation(sim)
```


### Figure 3:

Load data:

```{r}
load(file = "data/data_cobalt.Rdata")
```

Load functional group shapes:

```{r}
clamb <- readPNG("shapes/Benthic_invertebrate.png")
large_copepod <- readPNG("shapes/Large_MesoZoo.png")
small_copepod <- readPNG("shapes/Small_MesoZoo.png")
herring <- readPNG("shapes/Small_Pel_herring.png")
cod <- readPNG("shapes/Demersal.png")
tuna <- readPNG("shapes/Large_Pelagic_Tuna.png")
mictophid <- readPNG("shapes/Mesopelagic.png")
lanternfish <- readPNG("shapes/Midwater_predator.png")
```

Create functions:

```{r}
# Shelf simulations:
shelf_sim <- function(data) {
  out <- data.frame()
  sims <- list()
  
  for(i in 1:nrow(data)) {
    
    id <- data$id
    
    my_setup <- setupVertical2(szprod = data[i, 4], lzprod = data[i, 5], # Pelagic productivities
                               #bprodin = data[i, 3], # Benthic production
                               nStages = 9, # No. of size groups
                               depth = as.numeric(data[i, 2]), # Bottom depth
                               photic = 150, # Photic zone depth
                               mesopelagic = 250) # mesopelagic depth
    
    
    # Run FEISTY:
    sim <- simulateFEISTY(bCust    = F,
                          p      = my_setup, 
                          tEnd   = 200,
                          USEdll = TRUE) 
    
    
    
    # Take average biomass of the last 80 years:
    totBiomass <- sim$totBiomass %>%
      as.data.frame() %>%
      tail(80) %>%
      summarise(across(everything(), mean)) %>%
      rename(smallPel = totBiomass.smallPel,
             mesoPel = totBiomass.mesoPel,
             largePel = totBiomass.largePel,
             bathyPel = totBiomass.bathyPel,
             demersals = totBiomass.demersals) %>%
      t() %>%
      as.data.frame() %>%
      rename(totBiomass = V1) %>%
      rownames_to_column(var = "funGroup") %>%
      mutate(id = id[i])

    out <- rbind(out, totBiomass)
    sims[[i]] <- sim
    
  }
  
  out <- out %>%
    mutate(totBiomass = case_when(totBiomass == 0 ~ NA,
                                  T ~ totBiomass))
  
  return(list(sims = sims,
              Biomass = out))
}

# Create feeding flux from prey to predator:
getFeeding = function(sim) {
  p <- sim$p
  u <- sim$u
  
  # get last 40% of timeseries
  etaTime <- 0.4 
  ixTime  <- which(sim$t>=((1-etaTime)*sim$t[sim$nTime]))
  
  # Number of groups and biomass:
  ngroup <- p$ix[[length(p$ix)]][length(p$ix[[length(p$ix)]])] #resources (4) + fish 
  biomass <- u
  
  #Average of the biomass : 
  prey     <- colMeans(biomass[ixTime,]) # mean value of the last 40% time 
  predator <- colMeans(biomass[ixTime,]) # mean value of the last 40% time 
  
  # estimate encounters
  Enc <- p$V[1] * p$theta[1,] * prey 
  for (i in 2:length(predator)){
    Enc <- rbind(Enc, p$V[i] * p$theta[i,] * prey)
  }
  
  # estimate encounters per predator
  Encspecies = rowSums(Enc)
  
  # estimate the mortality generated
  mortpr <-  p$Cmax[1] * p$V[1] * p$theta[1,] / (p$Cmax[1]+ Encspecies[1]) * predator[1]
  for (i in 2:length(predator)){
    mortpr <- rbind(mortpr,p$Cmax[i] * p$V[i] * p$theta[i,] / (p$Cmax[i]+ Encspecies[i]) * predator[i])
  }
  
  # estimate the flux from prey to predator
  mortpr <- ifelse(is.na(mortpr),0,mortpr)
  flux_prey_to_pred <- t(t(mortpr)*prey)
  rownames(flux_prey_to_pred) <- paste("pred",colnames(p$theta),sep="_")
  colnames(flux_prey_to_pred) <- paste("prey",colnames(p$theta),sep="_")
  return(flux_prey_to_pred)
}

# Plot network function:
plotNetwork2 <- function(sim) {
  p=sim$p
  u=sim$u
  # Number of groups and biomass:
  ngroup <- p$ix[[length(p$ix)]][length(p$ix[[length(p$ix)]])] #ressources (4) + fish 
  biomass <- u# sim[,2:(p$ix[[length(p$ix)]][length(p$ix[[length(p$ix)]])]+1)] #ressources + poissons car se mangent entre eux (+1 car première colonne = temps)
  
  #Average of the biomass : 
  Bi <- colMeans(biomass[round(0.6 * nrow(biomass), digits = 0):nrow(biomass),]) # mean value of the last 40% time 
  
  if (p$setup == "setupBasic"){
    Av_depth <- c(-1,-1,-4,-4,0,0,-2,-2,-2,-3,-3,-3) # Vertical position
    
    p$SpId <- c('smallPel','largePel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])))
    
  }  
  
  if (p$setup == "setupBasic2"){
    Av_depth <- c(-1,-1,-4,-4,rep(0, length(p$ix[[1]])),rep(-2, length(p$ix[[2]])),rep(-3, length(p$ix[[3]])))
    
    p$SpId <- c('smallPel','largePel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])))
    
  }  
  
  
  if (p$setup == "setupVertical" | p$setup == "setupVertical2"){
    
    #Calculate average depth day/night
    Av_depth_day <- 1 : p$nStages
    Av_depth_night <- 1 : p$nStages
    for (i in 1:p$nStages) {
      Av_depth_day[i] <- which.max(p$depthDay[ ,i])
      Av_depth_night[i] <- which.max(p$depthNight[ ,i]) 
    }
    # this calculation takes the index of the matrix p$depthDay which actually represents the depth and the value corresponding to the index is the probability of finding x fish at this depth
    Av_depth <- -(Av_depth_day + Av_depth_night) / 2
    
    
    # Offset a bit for visualization:
    Av_depth[p$ix[[1]][1]:p$ix[[1]][length(p$ix[[1]])]] <- Av_depth[p$ix[[1]][1]:p$ix[[1]][length(p$ix[[1]])]] + 0.1 * p$bottom
    Av_depth[p$ix[[3]][1]:p$ix[[3]][length(p$ix[[3]])]] <- Av_depth[p$ix[[3]][1]:p$ix[[3]][length(p$ix[[3]])]] - 0.1 * p$bottom
    Av_depth[p$ix[[4]][1]:p$ix[[4]][length(p$ix[[4]])]] <- Av_depth[p$ix[[4]][1]:p$ix[[4]][length(p$ix[[4]])]] - 0.1 * p$bottom
    Av_depth[p$ix[[2]][1]:p$ix[[2]][length(p$ix[[2]])]] <- Av_depth[p$ix[[2]][1]:p$ix[[2]][length(p$ix[[2]])]] - 0.2 * p$bottom
    
    # Set color palette 
    p$SpId <- c('smallPel','mesoPel','largePel', 'bathyPel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])),
              rep(p$SpId[4], length(p$ix[[4]])),
              rep(p$SpId[5], length(p$ix[[5]])))
    
    # Specify depth axis text:
    yaxis <- c("Surface   ", "     Bottom")
    
  }
  
  # Marker size depends on biomass: 
  # Using real biomass yields bubbles with too many orders of magnitude difference.
  # Thus we apply a cubic square:
  Msize <- Bi / colMeans(example_sims[[1]]$u[round(0.6 * nrow(u), digits = 0):nrow(u), ])[1]
  Msize[Msize == 0] <- NA
  Msize <- Msize^(1/3)
  Max_size = max(Msize, na.rm = T)
  
  # Create line width: 
  Flux <- getFeeding(sim)
  Flux <- c(Flux) 
  threshold <- 0.05 # min(tail(sort(Flux), 100)) 
  indx <- which(Flux >= threshold) # takes the x highest values of theta
  
  
  # Set values of each coordinate and put them together:
  coord_1 <- data.frame(index = 1:p$nStages^2,
                        mc = rep(p$mc[1:p$nStages], p$nStages), 
                        depth = rep(Av_depth[1:p$nStages], p$nStages), 
                        SpId = rep(SpId, p$nStages),
                        Msize = rep(Msize, p$nStages), 
                        LineWdth = (Flux/max(Flux))^(1/3) / 15,
                        Alpha = (Flux/max(Flux))^(1/3))
  
  coord_2 <- data.frame(index = 1:p$nStages^2, # Notice that here repetition ys grouped by "each" to change order
                        mc = rep(p$mc[1:p$nStages], each = p$nStages), 
                        depth = rep(Av_depth[1:p$nStages], each = p$nStages), 
                        SpId = rep(SpId, each = p$nStages),
                        Msize = rep(Msize, each = p$nStages),
                        LineWdth = (Flux/max(Flux))^(1/3) / 15,
                        Alpha = (Flux/max(Flux))^(1/3))
  
  df <- rbind(coord_1, coord_2)
  
  df <- df %>% 
    arrange(desc(Msize))
  
  df2 <- df %>% filter(index %in% indx) %>%
    arrange(desc(Msize))
  
  if (length(p$ix)==3){
    p <- ggplot() +
      geom_line(data = df2, aes(x = mc, y = depth, group = index, size = LineWdth, color = SpId, alpha = Alpha), show.legend = F) +
      geom_point(data = df, aes(x = mc, y = depth, color = SpId, size = Msize), stroke = 0, shape = 16) +
      scale_color_manual(values = p$my_palette[attr(p$my_palette, "names") %in% df$SpId], 
                         labels = p$my_names[attr(p$my_palette, "names") %in% df$SpId]) +
      scale_radius(limits = c(0, NA), range = c(0, (8 * Max_size))) +
      # scale_size_area(max_size = 4, ) +
      scale_x_log10(breaks = trans_breaks("log10", function(x) 20^x),
                    labels = trans_format("log10", math_format(10^.x))) +
      scale_y_continuous(breaks = seq(0, round(-p$bottom - 1), by = -p$bottom), labels = yaxis) +
      labs(x ="Mass (g)", y = "", color = "Group") +
      theme_base() + 
      guides(size = "none") +
      theme(legend.position = "none",
            axis.title = element_text(size = 8),
            axis.text = element_text(size = 8),
            axis.text.x = element_blank(),
            axis.text.y = element_text(angle = 90, size = 8, hjust = .5, margin = margin(r = 0)),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(), 
            axis.ticks.y=element_blank(),
            axis.ticks.x = element_blank(),
            legend.text = element_text(size = 8))
  }
  
  if (length(p$ix)==5){
    p <- ggplot() +
      geom_line(data = df2, aes(x = mc, y = depth, group = index, size = LineWdth, color = SpId, alpha = Alpha), show.legend = F) +
      geom_point(data = df, aes(x = mc, y = depth, color = SpId, size = Msize), stroke = 0, shape = 16) +
      scale_color_manual(values = p$my_palette[attr(p$my_palette, "names") %in% df$SpId], 
                         labels = p$my_names[attr(p$my_palette, "names") %in% df$SpId]) +
      scale_radius(limits = c(0, NA), range = c(0, (8 * Max_size))) +
      # scale_size_area(max_size = 4, ) +
      scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                    labels = trans_format("log10", math_format(10^.x))) +
      scale_y_continuous(breaks = seq(0, round(-p$bottom - 1), by = -p$bottom), labels = yaxis) + 
      labs(x ="Mass (g)", y = "Depth (m)", color = "Group") +
      theme_base() + 
      guides(size = "none") +
      theme(legend.position = "none",
            axis.title = element_text(size = 8),
            axis.text = element_text(size = 8),
            axis.text.x = element_blank(),
            axis.text.y = element_text(angle = 90, size = 8, hjust = .5, margin = margin(r = 0)),
            axis.title.x = element_blank(),
            axis.title.y = element_blank(), 
            axis.ticks.y=element_blank(), 
            axis.ticks.x = element_blank(),
            legend.text = element_text(size = 8))
    
  }

  return(p)
}

# Make a network plot with x_axis:
plotNetwork3 <- function(sim) {
  p=sim$p
  u=sim$u
  # Number of groups and biomass:
  ngroup <- p$ix[[length(p$ix)]][length(p$ix[[length(p$ix)]])] #ressources (4) + fish 
  biomass <- u# sim[,2:(p$ix[[length(p$ix)]][length(p$ix[[length(p$ix)]])]+1)] #ressources + poissons car se mangent entre eux (+1 car première colonne = temps)
  
  #Average of the biomass : 
  Bi <- colMeans(biomass[round(0.6 * nrow(biomass), digits = 0):nrow(biomass),]) # mean value of the last 40% time 
  
  if (p$setup == "setupBasic"){
    Av_depth <- c(-1,-1,-4,-4,0,0,-2,-2,-2,-3,-3,-3) # Vertical position
    
    p$SpId <- c('smallPel','largePel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])))
    
  }  
  
  if (p$setup == "setupBasic2"){
    Av_depth <- c(-1,-1,-4,-4,rep(0, length(p$ix[[1]])),rep(-2, length(p$ix[[2]])),rep(-3, length(p$ix[[3]])))
    
    p$SpId <- c('smallPel','largePel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])))
    
  } 
  
  if (p$setup == "setupVertical" | p$setup == "setupVertical2"){
    
    #Calculate average depth day/night
    
    Av_depth_day <- 1 : p$nStages
    Av_depth_night <- 1 : p$nStages
    for (i in 1:p$nStages) {
      Av_depth_day[i] <- which.max(p$depthDay[ ,i])
      Av_depth_night[i] <- which.max(p$depthNight[ ,i]) 
      
    }
    #ce calcul prend l'indice de la matrice p$depthDay qui représente en réalité la profondeur et la valeur correspondant à l'indice est la probabilité de trouver x poisson à cette profondeur
    Av_depth <- -(Av_depth_day + Av_depth_night) / 2
    
    
    # Offset a bit for visualization:
    Av_depth[p$ix[[1]][1]:p$ix[[1]][length(p$ix[[1]])]] <- Av_depth[p$ix[[1]][1]:p$ix[[1]][length(p$ix[[1]])]] + 0.1 * p$bottom
    Av_depth[p$ix[[3]][1]:p$ix[[3]][length(p$ix[[3]])]] <- Av_depth[p$ix[[3]][1]:p$ix[[3]][length(p$ix[[3]])]] - 0.1 * p$bottom
    Av_depth[p$ix[[4]][1]:p$ix[[4]][length(p$ix[[4]])]] <- Av_depth[p$ix[[4]][1]:p$ix[[4]][length(p$ix[[4]])]] - 0.1 * p$bottom
    Av_depth[p$ix[[2]][1]:p$ix[[2]][length(p$ix[[2]])]] <- Av_depth[p$ix[[2]][1]:p$ix[[2]][length(p$ix[[2]])]] - 0.2 * p$bottom
    
    # Set color palette: 
    p$SpId <- c('smallPel','mesoPel','largePel', 'bathyPel', 'demersals')
    SpId <- c("smallZoo", "largeZoo", "benthos", "largeBenthos", 
              rep(p$SpId[1], length(p$ix[[1]])),
              rep(p$SpId[2], length(p$ix[[2]])),
              rep(p$SpId[3], length(p$ix[[3]])),
              rep(p$SpId[4], length(p$ix[[4]])),
              rep(p$SpId[5], length(p$ix[[5]])))
    
    # Specify depth axis text:
    yaxis <- c("Surface   ", "     Bottom")
    
  }
  
  # Marker size depends on biomass: 
  # Using real biomass yields bubbles with too many orders of magnitude difference.
  # Thus we apply a cubic square:
  Msize <- Bi / colMeans(example_sims[[1]]$u[round(0.6 * nrow(u), digits = 0):nrow(u), ])[1]
  Msize[Msize == 0] <- NA
  Msize <- Msize^(1/3)
  Max_size = max(Msize, na.rm = T)
  
  # Create line width: 
  Flux <- getFeeding(sim)
  Flux <- c(Flux) 
  threshold <- 0.05 # min(tail(sort(Flux), 100)) 
  indx <- which(Flux >= threshold) # takes the x highest values of theta
  
  
  # Set values of each coordinate and put them together:
  coord_1 <- data.frame(index = 1:p$nStages^2,
                        mc = rep(p$mc[1:p$nStages], p$nStages), 
                        depth = rep(Av_depth[1:p$nStages], p$nStages), 
                        SpId = rep(SpId, p$nStages),
                        Msize = rep(Msize, p$nStages), 
                        LineWdth = (Flux/max(Flux))^(1/3) / 15,
                        Alpha = (Flux/max(Flux))^(1/3))
  
  coord_2 <- data.frame(index = 1:p$nStages^2, # Notice that here repetition ys grouped by "each" to change order
                        mc = rep(p$mc[1:p$nStages], each = p$nStages), 
                        depth = rep(Av_depth[1:p$nStages], each = p$nStages), 
                        SpId = rep(SpId, each = p$nStages),
                        Msize = rep(Msize, each = p$nStages),
                        LineWdth = (Flux/max(Flux))^(1/3) / 15,
                        Alpha = (Flux/max(Flux))^(1/3))
  
  df <- rbind(coord_1, coord_2)
  
  df <- df %>% 
    arrange(desc(Msize))
  
  df2 <- df %>% filter(index %in% indx) %>%
    arrange(desc(Msize))
  
  if (length(p$ix)==3){
    p <- ggplot() +
      geom_line(data = df2, aes(x = mc, y = depth, group = index, size = LineWdth, color = SpId, alpha = Alpha), show.legend = F) +
      geom_point(data = df, aes(x = mc, y = depth, color = SpId, size = Msize), stroke = 0, shape = 16) +
      scale_color_manual(values = p$my_palette[attr(p$my_palette, "names") %in% df$SpId], 
                         labels = p$my_names[attr(p$my_palette, "names") %in% df$SpId]) +
      scale_radius(limits = c(0, NA), range = c(0, (8 * Max_size))) +
      # scale_size_area(max_size = 4, ) +
      scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                    labels = trans_format("log10", math_format(10^.x))) +
      scale_y_continuous(breaks = seq(0, round(-p$bottom - 1), by = -p$bottom), labels = yaxis) +
      labs(x ="Mass (g)", y = "", color = "Group") +
      theme_base() + 
      guides(size = "none") +
      theme(legend.position = "none",
            axis.title = element_text(size = 8),
            axis.text = element_text(size = 8),
            axis.text.y = element_text(angle = 90, size = 8, hjust = .5, margin = margin(r = 0)), 
            axis.title.y = element_blank(), 
            axis.ticks.y=element_blank(), 
            legend.text = element_text(size = 8))
  }
  
  if (length(p$ix)==5){
    p <- ggplot() +
      geom_line(data = df2, aes(x = mc, y = depth, group = index, size = LineWdth, color = SpId, alpha = Alpha), show.legend = F) +
      geom_point(data = df, aes(x = mc, y = depth, color = SpId, size = Msize), stroke = 0, shape = 16) +
      scale_color_manual(values = p$my_palette[attr(p$my_palette, "names") %in% df$SpId], 
                         labels = p$my_names[attr(p$my_palette, "names") %in% df$SpId]) +
      scale_y_continuous(breaks = seq(0, round(-p$bottom - 1), by = -p$bottom), labels = yaxis) + 
      scale_radius(limits = c(0, NA), range = c(0, (8 * Max_size))) +
      # scale_size_area(max_size = 4, ) +
      scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                    labels = trans_format("log10", math_format(10^.x))) +
      labs(x ="Mass (g)", y = "Depth (m)", color = "Group") +
      theme_base() + 
      guides(size = "none") +
      theme(legend.position = "none",
            axis.title = element_text(size = 8),
            axis.text = element_text(size = 8),
            axis.text.y = element_text(angle = 90, size = 8, hjust = .5, margin = margin(r = 0)), 
            axis.title.y = element_blank(), 
            axis.ticks.y=element_blank(), 
            legend.text = element_text(size = 8))
    
  }

  return(p)
}
```

Create depth-specific productivity based on COBALT outputs:

```{r}
# Edit COBALT data:
data_cobalt <- data_cobalt %>%
  filter(Temp_C > 5) %>%
  rename(benthos = ben_prod,
         smallZoo = mz_prod,
         largeZoo = lz_prod) %>%
  mutate(depth = round(depth, -1)) %>% # To get mean values for each 1-m interval
  group_by(depth) %>%
  summarise(benthos = mean(benthos),
            smallZoo = mean(smallZoo),
            largeZoo = mean(largeZoo))

# Model benthos:
m1 <- gam(benthos ~ s(depth),
          data = data_cobalt)

# Model small zooplankton:
m2 <- gam(smallZoo ~ s(depth),
          data = data_cobalt)

# Model large zoopankton:
m3 <- gam(largeZoo ~ s(depth),
          data = data_cobalt)

# Generate depth/productivity table:
#First generate a sequence of 100 values:
x <- seq(-10, 10, length.out = 100)

# Apply the logistic function to the sequence
logistic_values <- plogis(x) 
rm(x)

# Multiply by 3000 (m) and remove the first 70 m to generate the shelf:
depth <- (logistic_values * 2930) + 70

# Put depth in a new data frame:
df <- data.frame (id = 1:length(depth), depth) 

# Use models to predict benthic and zoo productivity:
df$benthos <- predict(m1, newdata = df)
df$smallZoo <- predict(m2, newdata = df)
df$largeZoo <- predict(m3, newdata = df)

# We want to show oligotrophic systems in open waters. Therefore, we apply a reduction factor for depths > 2000 m.
df <- df %>%
  mutate(factor = 1 + ((2000 - df$depth) / 1300),
         smallZoo = case_when(depth > 2000 ~ smallZoo * factor,
                              T ~ smallZoo),
         largeZoo = case_when(depth > 2000 ~ largeZoo * factor,
                              T ~ largeZoo))
```

Generate simulations:

```{r}
# Simulate shelf:
my_sims <- shelf_sim(df)

my_sims_biomass <- left_join(my_sims$Biomass, df, by = "id")

my_sims_biomass <- my_sims_biomass %>%
  mutate(depth2 = 3000 - depth)

# Pic specific examples:
examples <- c(19, 50, 90)
```

Create shelf plot:

```{r}
#| warning: FALSE
# Upper trophic levels:
p3a <- ggplot(data = my_sims_biomass) +
  geom_line(aes(x = id, y = (totBiomass), color = funGroup), size = .7, alpha = .9) +
  scale_color_manual(values = my_sims$sims[[1]]$p$my_palette[attr(my_sims$sims[[1]]$p$my_palette, "names") %in% my_sims_biomass$funGroup], 
                         labels = my_sims$sims[[1]]$p$my_names[attr(my_sims$sims[[1]]$p$my_palette, "names") %in% my_sims_biomass$funGroup]) +
  geom_area(aes(x = id, y = 1/1000 * depth2, alpha = 0), fill = "burlywood4", alpha = 0.2) +
  geom_vline(xintercept = examples, alpha = .7, linetype = "dotted") +
  annotate("text", label = c("c", "d", "e"), x = examples + 2, y = 22, size = 3) +
  annotation_raster(herring, xmin = examples[[2]] + 10, xmax = examples[[2]] + 25, 
                    ymin = 20, 
                    ymax = 18, interpolate = T) +
  annotation_raster(tuna, xmin = examples[[2]] + 8, xmax = examples[[2]] + 28,  
                    ymin = 15, 
                    ymax = 18, interpolate = T) +
  annotation_raster(mictophid, xmin = examples[[2]] + 10, xmax = examples[[2]] + 25,  
                    ymin = 13, 
                    ymax = 15, interpolate = T) +
  annotation_raster(lanternfish, xmin = examples[[2]] + 8, xmax = examples[[2]] + 28,  
                    ymin = 11, 
                    ymax = 13, interpolate = T) +
  annotation_raster(cod, xmin = examples[[2]] + 8,  xmax = examples[[2]] + 28,  
                    ymin = 9, 
                    ymax = 11, interpolate = T) +
  ylab(expression(paste("Biomass (g ", m^-2,")"))) +
  theme_base() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.position = "none", #c(.7, 0.65),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA)) +
  guides(color = guide_legend(ncol = 1))

# Resources:
df2 <- df %>% pivot_longer(cols = 3:5, names_to = "resource") %>%
  rename(productivity = value)

# Specify depth axis text:
xaxis <- c("Shelf", "Slope", "Open ocean")

p3b <- ggplot(data = df2) + 
  geom_line(aes(x = id, y = productivity, color = resource), size = .7, alpha = .8) +
  scale_color_manual(values = my_sims$sims[[1]]$p$my_palette[attr(my_sims$sims[[1]]$p$my_palette, "names") %in% df2$resource], 
                     labels = my_sims$sims[[1]]$p$my_names[attr(my_sims$sims[[1]]$p$my_palette, "names") %in% df2$resource]) +
  geom_vline(xintercept = examples, alpha = .7, linetype = "dotted") +
  
  annotation_raster(small_copepod, xmin = examples[[2]] + 18.2,  xmax = examples[[2]] + 25.2,  
                    ymin = 76, 
                    ymax = 92, interpolate = T) +
  annotation_raster(large_copepod, xmin = examples[[2]] + 16,  xmax = examples[[2]] + 27,  
                    ymin = 50, 
                    ymax = 75, interpolate = T) +
  annotation_raster(clamb, xmin = examples[[2]] + 17.5,  xmax = examples[[2]] + 25.5,  
                    ymin = 24, 
                    ymax = 46, interpolate = T) +
  
  scale_x_continuous(breaks = examples, labels = xaxis) +
  ylab(expression(paste("Resources (g ", m^-2," yr)")))  +
  theme_base() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.position = "none", #c(.5, -.17),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA)) +
  guides(color = guide_legend(nrow = 2))

```

Create network plots:

```{r}
# Select example simulations:
example_sims <- my_sims$sims[df[examples, ]$id]

p3c <- plotNetwork2(example_sims[[1]])
p3d <- plotNetwork2(example_sims[[2]])
p3e <- plotNetwork3(example_sims[[3]])

```

Combine panels in a single plot:

```{r}
#| warning: FALSE
# Layout plot:
layout <- "
AAC
AAD
BBE
"

p <- p3a + p3b + p3c + p3d + p3e + plot_layout(design = layout)  &
  theme(plot.background = element_blank(), plot.margin = margin(0, 1, 0, 1, "mm") ) &
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 10))

p
```

Export plot:

```{r}
#| warning: FALSE
ggsave("plots/plot3.pdf", p, height = 100 , width = 160, units = "mm", scale = 1)
```

### Figure 4:

Stage sensitivity run:

```{r}
experiment = seq(3, 27, 3) # number of stages

iFish <- c(1,2,3,4,5) # 1:smallPel  2:mesoPel 3:largePel  4:bathyPel  5:demersal
df_m <- matrix(ncol = length(iFish) + 1,
               nrow = length(experiment))

# Stage loop
Stages <- c()
i <- 1
for (test in experiment)
{
  param <- setupVertical2(depth = df[examples[2], "depth"],
                          szprod = df[examples[2], "smallZoo"],
                          lzprod = df[examples[2], "largeZoo"],
                          bent =  121 + 2.58*df[examples[2], "benthos"], # conversion from benthic production to flux
                          nStages = test)

  sim <- simulateFEISTY(p = param, tEnd = 200, bCust = TRUE)
  df_m[i,] <- c(apply(sim$totBiomass[121:201,], 2, mean), test)
  
  i <- i+1
}

# Massage into long format df
dimnames(df_m) <- list(NULL, c(p$my_names[4 + iFish], "Stages"))
df_stage <- pivot_longer(as.data.frame(df_m), cols = unname(p$my_names[4 + iFish]))
```

Stage sensitivity plotting:

```{r}
p4a <- ggplot(transform(df_stage,
                      name = factor(name, levels = param$my_names))) +
  geom_line(aes(x=Stages, y=value, color = name), linetype  = 1) +
  geom_point(aes(x=Stages, y=value, color = name)) +
  annotation_raster(herring, xmin = 21, xmax = 21+4, 
                    ymin = 2.75, 
                    ymax = 3.25, interpolate = T) +
  annotation_raster(tuna, xmin = 21, xmax = 21+4, 
                    ymin = 4.5, 
                    ymax = 4, interpolate = T) +
  annotation_raster(mictophid, xmin = 21, xmax = 21+4, 
                    ymin = 6.25, 
                    ymax = 6.75, interpolate = T) +
  annotation_raster(lanternfish, xmin = 21, xmax = 21+4, 
                    ymin = 1.75, 
                    ymax = 2.25, interpolate = T) +
  annotation_raster(cod, xmin = 21, xmax = 21+4, 
                    ymin = 0.25, 
                    ymax = 0.75, interpolate = T) +
  scale_x_continuous(breaks = unique(df_stage$Stages),
                     name = "Number of stages") +
  scale_y_continuous(name = expression("Biomass (gww⋅"*m^-2* ")" )) +
  scale_color_manual(values = c("#EE6677",  "#AA4499", "#33BBEE", "#004488", "#228833")) + # fix this to use palette
  theme_base() +
  theme(axis.text.x = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.position = "none", 
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA)) +
  guides(color = guide_legend(ncol = 2))
```

Setup sensitivity run:

```{r}
df$benthic_flux <- 121 + (2.58*df$benthos) # conversion from benthic production to flux

# Experiment
experiment <- seq(1, nrow(df), 1)

# Initialization
df_m <- matrix(ncol = 4 + 1,
               nrow = length(experiment))

# Stage number loop
i <- 1
for (test in experiment)
{
  param1 <- setupBasic(szprod = df$smallZoo[test],
                       lzprod = df$largeZoo[test],
                       bprod  = df$benthos[test],
                       depth  = df$depth[test]) 
  param2 <- setupBasic2(szprod = df$smallZoo[test],
                        lzprod = df$largeZoo[test],
                        bprod  = df$benthos[test],
                        depth  = df$depth[test]) 
  param3 <- setupVertical(szprod = df$smallZoo[test],
                          lzprod = df$largeZoo[test],
                          bent = df$benthic_flux[test],
                          depth  = df$depth[test]) 
  param4 <- setupVertical2(szprod = df$smallZoo[test],
                           lzprod = df$largeZoo[test],
                           bent = df$benthic_flux[test],
                           depth  = df$depth[test],
                           nStages = 9)

  sim1 <- simulateFEISTY(p = param1, tEnd = 200, bCust = TRUE)
  sim2 <- simulateFEISTY(p = param2, tEnd = 200, bCust = TRUE)
  sim3 <- simulateFEISTY(p = param3, tEnd = 200, bCust = TRUE)
  sim4 <- simulateFEISTY(p = param4, tEnd = 200, bCust = TRUE)
  
  bmass1 <- sum(apply(sim1$totBiomass[121:201,], 2, mean))
  bmass2 <- sum(apply(sim2$totBiomass[121:201,], 2, mean))
  bmass3 <- sum(apply(sim3$totBiomass[121:201,], 2, mean))
  bmass4 <- sum(apply(sim4$totBiomass[121:201,], 2, mean))
  
  df_m[i, ] <- c(bmass1, bmass2, bmass3, bmass4, df$depth[test])
  
  i <- i+1
}

# Massage into long format df
dimnames(df_m) <- list(NULL, c("Basic", "Basic2", "Vertical", "Vertical2", "Depth"))
df_setup <- pivot_longer(as.data.frame(df_m), cols = !Depth)
```

Setup sensitivity plotting:

```{r}
p4b <- ggplot(transform(df_setup,
                      name = factor(name, levels = c("Basic", "Basic2", "Vertical", "Vertical2")))) +
  geom_line(aes(x=Depth, y=value, linetype = name)) +
  scale_y_continuous(name = expression("Biomass (gww⋅"*m^-2* ")" )) +
  scale_linetype_manual(values = c("solid", "dotted", "longdash", "dotdash")) +
  theme_base() +
  theme(axis.text.x = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.position=c(0.65, 0.85),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA)) +
  guides(linetype = guide_legend(nrow = 2))
```

Combine panels into a single plot:

```{r}
#| warning: FALSE
# Layout plot:
layout <- "
AB
"

p4 <- p4a + p4b + plot_layout(design = layout)  &
  theme(plot.background = element_blank(), plot.margin = margin(0, 1, 0, 1, "mm") ) &
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 10))

p4
```

### Figure 5:

Load global forcing data and world shape:

```{r}
#| warning: FALSE
load(file = "data/Input_global.Rdata")
world <- rnaturalearth::ne_countries(scale = 10, returnclass = "sf")
```

Create a function to run FEISTY in parallel:

```{r}
#| warning: FALSE
# Set cores:
cl <- makeCluster(detectCores() - 2) 
registerDoParallel(cl)

# Create function:
simulateFEISTY_parallel <- function(rowidx, glob) {
  sim = simulateFEISTY(
    p = setupVertical2(
      szprod = glob[rowidx, "szprod"],
      lzprod = glob[rowidx, "lzprod"],
      dfbot  = glob[rowidx, "dfbot"],
      photic = glob[rowidx, "photic"],
      depth  = glob[rowidx, "depth"],
      Tp     = glob[rowidx, "Tp"],
      Tm     = glob[rowidx, "Tm"],
      Tb     = glob[rowidx, "Tb"]), 
    tEnd = 300) # nb of years to simulate model run
  return(sim)
}
```

Run global model in parallel:

```{r}
#| warning: FALSE
# Create empty list
res         <- list()
all_results <- list()

# Run model:
all_results <- foreach(rowidx = 1:nrow(glob), .packages = c("FEISTY")) %dopar% {
  sim = simulateFEISTY_parallel(rowidx, glob)
  res$lon=glob[rowidx,"lon"]
  res$lat=glob[rowidx,"lat"]
  res$totBiomass=colMeans(sim$totBiomass[round(0.6*sim$nTime):sim$nTime,]) # last 40% simulate time
  return(res)
}

stopCluster(cl)

# Create a data frame
out <- t(data.frame(matrix(data=unlist(all_results),nrow=7)))
colnames(out) <- c("lon","lat","totB_smpel","totB_mesopel","totB_largepel","totB_bathypel", "totB_dem")
out <- as.data.frame(out)
```

Prepare output data for plotting:

```{r}
#| warning: FALSE
# Get output
out$tot <- rowSums(out[,3:7])
out$lon <- ifelse(out$lon > 179.5,out$lon-360,out$lon)
out_sf  <- st_as_sf(out, coords = c("lon","lat"),crs = 4326)

# Create grid
grid <- st_as_sf(out_sf %>% 
          st_make_grid(cellsize = 1, what = "polygons")) %>% 
          st_join(out_sf, join = st_intersects, left = TRUE)
```

Plot it out:

```{r}
#| warning: FALSE
p <- ggplot(grid) + 
  geom_sf( aes(fill=log10(tot+0.01)), colour = NA ) + 
  scale_fill_viridis(name="Fish biomass g m-2 /n  \n",
                     labels = c("<0.01","1","100"),breaks=c(-2,0,2))  + 
  geom_sf(data=world,col="#8c8c8c",fill="#f2f2f2") +
  coord_sf(crs= "+proj=moll") +
  theme(plot.background=element_blank(),
        panel.background=element_blank(),
        axis.text.y   =element_blank(),
        axis.text.x   =element_blank(),
        axis.ticks    = element_blank(),
        axis.title.y  =element_blank(),
        axis.title.x  =element_blank(),
        panel.border  = element_blank(),
        legend.position = "bottom",
        legend.title = element_text(size=8))

p
```

Export plot:

```{r}
#| warning: FALSE
ggsave("plots/plot5.pdf", p, height = 3.5 , width = 5)
```

### Figure 6:

Define fishing loop function:

```{r}
simFishing <- function(param, group, F_list)
{
  bmass <- c()
  yield <- c()
  df_fishing <- data.frame()
  
  for (Fi in F_list) # F loop
  {
    q <- setFishing(param, F=Fi, groups=group, etaF=0.05)
    sim <- simulateFEISTY(p = q, tEnd = 200, bCust = TRUE)
    
    bmass <- c(bmass, mean(sim$totBiomass[121:201, group]))
    yield <- c(yield, mean(sim$yield[121:201, group]))
  }
  
  df_fishing <- data.frame(F = F_list,
                           Biomass = bmass / max(bmass),
                           Yield = yield / max(yield))

  return(df_fishing)
}
```

Fishing simulations:

```{r}
iFish <- c(1,2,3,4,5) # 1:smallPel  2:mesoPel 3:largePel  4:bathyPel  5:demersal
param <- setupVertical2(depth = df[examples[1], "depth"],
                        szprod = df[examples[1], "smallZoo"],
                        lzprod = df[examples[1], "largeZoo"],
                        bent =  121 + 2.58*df[examples[1], "benthos"],
                        nStages = 9)

df_fishing_smallPel <- simFishing(param, 1, seq(0, 6, 0.2))
df_fishing_largePel <- simFishing(param, 3, seq(0, 0.075, 0.0005))
df_fishing_demersal <- simFishing(param, 5, seq(0, 1.75, 0.01))
```

Plotting panels:

```{r}
p6a <- ggplot(df_fishing_smallPel) +
  aes(x = F) +
  geom_line(aes(y=Biomass), color=q$my_palette[1+4], linetype=1) + # 1: smallPel
  geom_line(aes(y=Yield), color=q$my_palette[1+4], linetype  = 2) + # 1: smallPel
  scale_x_continuous(name = expression("Fishing mortality "*italic(F)*" ("*yr^-1 *")"),
                     breaks = c(min(df_fishing_smallPel$F), max(df_fishing_smallPel$F))) +
  scale_y_continuous(name = "Relative to maximum",
                     breaks = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)) +
  theme_base() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        legend.title = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA))

p6b <- ggplot(df_fishing_largePel) +
  aes(x = F) +
  geom_line(aes(y=Biomass), color=q$my_palette[3+4], linetype=1) + # 3: largePel
  geom_line(aes(y=Yield), color=q$my_palette[3+4], linetype  = 2) + # 3: largePel
  scale_x_continuous(name = expression("Fishing mortality "*italic(F)*" ("*yr^-1 *")"),
                     breaks = c(min(df_fishing_largePel$F), max(df_fishing_largePel$F))) +
  theme_base() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA))

p6c <- ggplot(df_fishing_demersal) +
  aes(x = F) +
  geom_line(aes(y=Biomass), color=q$my_palette[5+4], linetype=1) +  # 5: demersal
  geom_line(aes(y=Yield), color=q$my_palette[5+4], linetype  = 2) + # 5: demersal
  scale_x_continuous(name = expression("Fishing mortality "*italic(F)*" ("*yr^-1 *")"),
                     breaks = c(min(df_fishing_demersal$F), max(df_fishing_demersal$F))) +
  theme_base() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.key = element_rect(colour = NA, fill = NA))
```

Combine panels into a single plot:

```{r}
#| warning: FALSE
# Layout plot:
layout <- "
ABC
"

p6 <- p6a + p6b + p6c + plot_layout(design = layout)  &
  theme(plot.background = element_blank(), plot.margin = margin(0, 1, 0, 1, "mm") ) &
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(size = 10))

p6
```

Export plot:

```{r}
#| warning: FALSE
ggsave("plots/plot6.pdf", p6, height = 40 , width = 80, units = "mm", scale = 1)
```

### Figure S1:

### Figure S2:

### Figure S3:
